---
title: "Nonlinear Temperature Effects Indicate Severe Damages to Quebec Forestry Harvest Volume Under Climate Change" 
author: 
  - Jinqi Guo 
  - Young Joseph Chung 
  - Steven 
date: today 
date-format: "MMM D, YYYY" 
subtitle: "Supporting Information Appendix"
format: 
  pdf: 
    documentclass: article 
    geometry: margin = 1in 
    toc: true 
    number-sections: true 
    colorlinks: true 
    lof: true 
    lot: true 
    thanks: " Code and data are avaiable at: https://github.com/UtopianYoungChung/GDP-Temperature.git" 
bibliography: bibliography.bib 
---

# Data Appendix

## Dependent Variable

Harvest volume for Logs and bolts, Pulpwood, and FuelWood for the years 1990-2019 are reported by the Forestry Department.

```{r setup, include= FALSE}
library(tidyverse)
library(palmerpenguins)
library(knitr)
library(dplyr)
library(ggplot2)
library(psych)

```

```{r}
#| messages: false
#| echo: false
#| warning: false
#| label: tbl-1
#| tbl-cap: Descritpive Statistics Harvest Volume

### Read and merge datasets ###
gdp <- read_csv(here::here("inputs/data/GDP/Forestry/gdp.csv"), show_col_types = FALSE)

### renaming Fuelwood*b to FuelWood###

gdp <- gdp %>% 
  mutate(Category = case_when(
    Category == "Fuelwood*b and firewood*c" ~ "FuelWood (Volume/hec)",
    Category == "Logs and bolts" ~ "Logs (Volume/hec)",
    Category == "Pulpwood" ~ "PulpWood (Volume/hec)",
    TRUE ~ Category
  ))

# Constants for conversion
total_hectares = 198990

# Calculate summary statistics for each category
summary_gdp_stats <- gdp %>%
  select(Category, `Volume (cubic metres) (En) Nulls`) %>%
  group_by(Category) %>%
  summarise(
    #Total_Volume = sum(`Volume (cubic metres) (En) Nulls`, na.rm = TRUE),
    Mean = mean(`Volume (cubic metres) (En) Nulls`, na.rm = TRUE)/total_hectares,
    Minimum = min(`Volume (cubic metres) (En) Nulls`, na.rm = TRUE)/total_hectares,
    Maximum = max(`Volume (cubic metres) (En) Nulls`, na.rm = TRUE)/total_hectares,
    Std = sd(`Volume (cubic metres) (En) Nulls`, na.rm = TRUE)/total_hectares
  )
summary_gdp_stats %>% 
  kable()

```

# Regression Models

# Regression Results and Significance Levels

# Out-ofSample Prediction Accuracy

# Nonlinearities and Climate Change Impacts

# Cross-section versus Time Series

# Temporal Subsets

# Temperature - Precipitation Interaction

# Growing Season and Time Separability

# Year Fixed Effects

# Linear Within-Day Temperature Interporation

# Unifom Climate Change Scenarios
